No sign of recovery

### 2018-05-21 Manuscript.Rmd
Are new or extinct species a random selection from the species that were recorded at the site oder are them specific in terms of Ellenberg value?

```{r}
x <- 28

getsamples <- function(s, nspec, d) {
  sample(d$T, nspec, replace = FALSE) %>% mean(na.rm = TRUE)
}

getsim <- function(x) {
  tt <- pl %>% filter(aID_STAO == x) %>% 
    group_by(aID_SP, T, F, N, L) %>% 
    summarise(Occ1 = sum(Visit == 1),
              Occ2 = sum(Visit == 2),
              Occ3 = sum(Visit == 3))
  gain <- (tt$Occ1 == 0 & tt$Occ2 == 1) | (tt$Occ2 == 0 & tt$Occ3 == 1)
  lost <- (tt$Occ1 == 1 & tt$Occ2 == 0) | (tt$Occ2 == 1 & tt$Occ3 == 0)
  tmpgain <- map_dbl(1:nsim, getsamples, nspec = sum(gain), d = tt)
  tmplost <- map_dbl(1:nsim, getsamples, nspec = sum(lost), d = tt)
  list(
    gain = mean(tt$T[gain], na.rm = TRUE),
    gainran = mean(tmpgain, na.rm = TRUE),
    gainransd = sd(tmpgain, na.rm = TRUE),
    lost = mean(tt$T[lost], na.rm = TRUE),
    lostran = mean(tmplost, na.rm = TRUE),
    lostransd = sd(tmplost, na.rm = TRUE))
}

tt <- map(sites$aID_STAO, getsim)

sites$ngain <-  tt %>% map_dbl(function(x) (x$gain - x$gainran))
sites$nlost <-  tt %>% map_dbl(function(x) (x$lost - x$lostran))

>>>>

```{r}
# Functions 
getsamples <- function(s, nspec, d, EL) {
  sample(d %>% pull(paste(EL)), nspec, replace = FALSE) %>% mean(na.rm = TRUE)
}

getsim <- function(x, EL, gain) {
  tt <- pl %>% filter(aID_STAO == x) %>% 
    group_by(aID_SP, T, F, N, L) %>% 
    summarise(Occ1 = sum(Visit == 1),
              Occ2 = sum(Visit == 2),
              Occ3 = sum(Visit == 3))
  if(gain)  ausw <- (tt$Occ1 == 0 & tt$Occ2 == 1) | (tt$Occ2 == 0 & tt$Occ3 == 1)
  if(!gain) ausw <- (tt$Occ1 == 1 & tt$Occ2 == 0) | (tt$Occ2 == 1 & tt$Occ3 == 0)
  tmp <- map_dbl(1:nsim, getsamples, nspec = sum(ausw), d = tt, EL = EL)
  list(
    nchange = sum(ausw),
    meanreal = mean(tt[ausw, paste(EL)] %>% unlist, na.rm = TRUE),
    mean = mean(tmp, na.rm = TRUE),
    lower = quantile(tmp, probs = 0.025, na.rm = TRUE),
    upper = quantile(tmp, probs = 0.975, na.rm = TRUE))
}

res <- sites %>% 
  filter(NTOT < 4) %>% 
  transmute(aID_STAO = aID_STAO, Sitemeasure = NTOT)
tmp <- map(res$aID_STAO, getsim, EL = "N", gain = TRUE)
res$meanreal <- tmp %>% map_dbl("meanreal")
res$mean <- tmp %>% map_dbl("mean")
res$lower <- tmp %>% map_dbl("lower")
res$upper <- tmp %>% map_dbl("upper")
ggplot(res, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black", alpha = 0.4) +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey", alpha = 0.4)

res1 <- rbind(
  res %>% transmute(aID_STAO = aID_STAO, Sitemeasure = Sitemeasure, mean = mean, type = "Sample"),
  res %>% transmute(aID_STAO = aID_STAO, Sitemeasure = Sitemeasure, mean = meanreal, type = "Real"))
mod1 <- lmer(mean ~ Sitemeasure * type + (1|aID_STAO), data = res1)
mod2 <- lmer(mean ~ Sitemeasure + type + (1|aID_STAO), data = res1)
anova(mod1, mod2)

summary(glmer(SR ~ yr * NTOT + (yr|aID_STAO), data = surv, family = "poisson"))
mod1 <- lmer(N ~ yr * NTOT + (yr|aID_STAO), data = surv)
mod2 <- lmer(N ~ yr + NTOT + (yr|aID_STAO), data = surv)
anova(mod1, mod2)
